User-customized hashtag/tag prediction on Twitter and StackOverflow:\protect \\ Comparing vector-based and Bayesian models of tag retrieval

### 2013-10-02 writeups/proposal/proposal.tex
foo
Former-commit-id: ee9bd784e6616ba2049508e5c06dfb566ee9917d [formerly c6f962873f33d5ee75847827c25798da710f6ce2]
Former-commit-id: e5cf7845ecd171f0c6a1785f7f2a6d56f3064e71
foo
Former-commit-id: 941fac6cfa638da1c86adf4375e78db2d713ccba [formerly 2b9ea25b5467859f16af5847215affdac94198c3]
Former-commit-id: 7af1cf806d7237a1d09cf5046caca536d2bfcaa7

\documentclass[man,floatsintext]{apa6}

@@

\title{FIXME}
\shorttitle{}

@@

Random permutations uses one of simplest permutations possible to create a new environment vector.
This operation is much less costly than circular convolution used by the BEAGLE model, which allows random permutations to scale better and handle larger datasets.
However, even though random permutations is a simpler representation than BEAGLE, it also performs better when trained on the same sized corpus.

>>>>

\documentclass[man,floatsintext,donotrepeattitle]{apa6}

@@

\title{User-customized hashtag/tag prediction on Twitter and StackOverflow:\protect \\ Comparing vector-based and Bayesian models of tag retrieval}
\shorttitle{Tag prediction on Twitter and StackOverflow}

@@

Random permutations uses one of simplest permutations possible to create a new environment vector.
This operation is much less costly than circular convolution used by the BEAGLE model, which allows random permutations to scale better and handle larger datasets.
Further, even though random permutations is a simpler representation than BEAGLE, it also performs better when trained on the same sized corpus.
